The shape of kelp: environmental influences on kelp morphology

### 2018-10-29 chapter_2.Rmd
results section added for new morphology comparison section

>>>>

When comparing morphologies bewteen deep and shallow water _Ecklonia maxima_ individuals, clear pattern is seen in certian morphological characteristics. These are frond length, frond mass, primary length, primary width and stipe circumference, and all show a similar pattern. Significant differences in these morphological characterstics at Kommetjie and Soetwater are evident, however there are no significant differences from Buffel's Bay to Kalk Bay.
